### 2018-10-23 Old_Latex/ArticleNew.tex
Update Erik's files

The shallow water (SW) equations  have been widely used to study basic
mechanisms occurring in geophysical flows \cite[see for
example][]{VallisLIVRE2006}.
%
The equations are based on the hydrostatic approximation which is
extremely well satisfied for a very wide range of scales in the oceans
and in the atmosphere.  They also rely on a stronger hypothesis
regarding the density stratification.  The fluid is assumed to be
structured in a limited number of thin homogeneous layers, which leads
to equations involving only two-dimensional operators. The two-layer
SW equations capture the baroclinic instability which is of
primary importance for the dynamics of the oceans and of the
atmosphere \cite[]{VallisLIVRE2006, Wirth2013}.
%
The single layer SW equations are very similar to
the two-dimensional compressible Navier-Stokes equations.  The
equations do not capture baroclinic instability but they constitute
one of the simplest hydrodynamic models with coexisting eigenmodes of
the linearized operator with zero linear frequency and with finite
non-zero linear frequency, $\omega  \pm\sqrt{f^2 + c^2
k^2}$, where $f$ is the Coriolis parameter, $c$ the gravity wave speed and $k
= |\kk|$ the wave number.
%

@@

Some predictions are based on the weak wave turbulence formalism
\cite[]{ZakharovLvovFalkovich1992, Nazarenko2011}. In the case of
inertia-gravity waves, \cite{FalkovichMedvedev1992} showed that the exact
solutions of the kinetic equation corresponding to a constant downscale energy
flux is associated with a spectrum scaling as $E(k) \sim k^{-8/3}$, while
\cite{ZakharovSagdeev1970} used weak turbulence formalism to derive a spectrum
of the form $ E(k) \sim k^{-3/2} $ for acoustic turbulence. This prediction is
of particular interest, since the aqoustic equations and the SW equations are
identical when a first order expansion is made in density or displacement
pertubations. It may be questioned, however, that weak turbulence formalism is
applicable to acoustic and SW wave turbulence, no matter how weak the
nonlinearities are supposed to be. As pointed out by \cite{KadomtsevPet1970}
and \cite{FalkovichMeyer1996}, when dispersion is small enough, waves moving in
the same direction have the same velocity and interact strongly, which leads to
the formation of shocks. In this case, the weak wave turbulence formalism is
unable to give valuable results. Such sharp and long structures have been
observed in many simulations \cite[]{FargeSadourny1989,
PolvaniMcWilliamsSpallFord1994, LahayeZeitlin2012} but their effects are not
well understood.
%
As shown by \cite{Burgers1948} the energy spectrum of a flow dominated by
shocks will scale as $ k^{-2} $, a prediction which has been confirmed by a
great number of simulations of Burgers equation \cite[for a review, see ]
[]{Frisch2001}. The shocks also lead to very strong intermittency, as
demonstrated by \cite{BouchaudMezardParisi1995} and
\cite{WeinanKhaninMazelSinai1997} for Burgers turbulence.
%
\cite{FalkovichMeyer1996} simulated acoustic turbulence dominated by shocks
and reported spectra scaling as $ k^{-2} $.
\cite{YuanHamilton1994} carried out
forced dissipative simulations of the SW equations showing similar spectra.
However, the resolution in both these studies was quite coarse, ($386^2$
and $101^2$ grid points, respectively) so that the scaling range was very
narrow.  Moreover, \cite{FalkovichMeyer1996} used a very particular
type of strongly anisotropic forcing with waves in only one
direction while \cite{YuanHamilton1994} forced in geostrophic modes
which severely complicates the interpretation.

@@

We have carried out a theoretical and numerical investigation of SW wave
turbulence. First, we derived the SW analogue (\ref{eq_Kolmo}) of the the
`four-fifths' law of Kolmogorov turbulence. Using this relation and
straightforward statistical and geometrical arguments we developed a simple
shock model predicting that the shock amplitude scales as $ (\epsilon d)^{1/3}
$, where $ d $ is the mean distance between the shocks, and that the $ p $:th
order structure function above a certain minimum will scale as $ (\epsilon
d)^{p/3} r/d $. Then, we carried out a series of twenty forced dissipative
simulations, varying the Froude number and the resolution. In all simulations,
a statistically stationary state were reached and in all simulations we
observed shocks. The flow variables in each Fourier mode were found to evolve
in accordance with linear wave dynamics, with equipartition between APE and KE
over a period. The third order structure function relation was fulfilled with a
high degree of accuracy. From the simulations we made two interesting
observations that fall outside the predictive range of the model. The first
observation was that mean energy in the stationary state approximately scales
as (\ref{MeanEnergy}), suggesting that the normalised dissipation
(\ref{Dissipation}) will go to zero both in the limit of small viscosity and
large wave speed. This is different from three dimensional Kolmogorov
turbulence as well as strongly stratified turbulence, where, in both cases,
dissipation is finite in the limit of small viscosity, and in the latter case
also is independent of the degree of stratification. This observation suggests
that SW wave turbulence does not fit into the paradigm of a local
Richardson-Kolmogorov cascade. The second observation we made was that the mean
distance between the shocks scales as $ c^{-1/2} $, if the other parameters are
held constant. As we increased $ c $, the shocks were thus becoming denser.
Using this observation we tested the shock model by plotting the normalised and
compensated structure functions of different orders. Generally we found that
there was a quite good agreement between the simulation results and the model
predictions, becoming better with decreasing wave speed and increasing
resolution.

@@

The question that originally motivated this study was if SW wave turbulence can
be used as a model for energy dissipation in the the atmosphere and the oceans.
Undoubtedly, the answer to this question is negative and the reason for this is
not primarily the appearance of shocks and the associated $ k^{-2} $-spectrum
which is not consistent with the observed $ k^{-5/3} $-spectrum. The main
reason is that SW wave turbulence is a far too inefficient agent of
dissipation. Since the Reynolds number of geophysical flows is extremely large
and the stratification is strong, the relation (\ref{Dissipation}) implies that
dissipation would be absent in the interior of the atmosphere and the oceans
with SW turbulence as the responsible agent. This not what we observe.

Although the answer to the question that originally motivated this study is
negative, it may lead us or some other investigators to pursue another
interesting research direction. As pointed out in the introduction, the
acoustic equations are to the lowest order expansion in density pertubations
identical to the SW equations. This study may therefore give important clues to
the long standing problem of acoustic turbulence, in two and three dimensions.
A similar shock model as we developed in two dimensions may easily be
formulated in three dimensions, where the third order structure function law
will be similar to (\ref{eq_Kolmo}), with the only difference that the constant
$ 4 $ on the right hand side should be replaced by $ 8/3 $. In three dimensions
we find
\begin{equation}
\meane{ |\delta \uu|^2 \delta J_L }
+ c^2\meane{ (\delta h)^2 \delta u_L } = - \frac{8}{3} \varepsilon r. \label{eq_Kolmo3}
\end{equation}
In the case of acoustic turbulence $ \delta h $ should be interpreted as a
normalised density increment rather than a displacement increment. If shocks in
three dimensions are assumed to form as smooth surfaces rather than smooth
lines, then the mean distance, $ d $, between the shocks will appear in the
model as $ d \sim {\cal{V}}/A_s $, where $ A_{s} $ is the total shock area and
$ \cal{V} $ is the volume of the domain. The shock amplitude will thus scale as
$ (\epsilon d)^{1/3} $ and the structure functions will scale as $ (\epsilon
d)^{p/3} r/d $ also in three dimensions, provided, of course, that shocks will
form in a similar way as in two dimensions. If they do, the most interesting
questions are if the mean energy and the mean distance between the shocks scale
in a similar way in three dimensions as in two dimensions. Simulations or
experiments of acoustic turbulence may provide answers to these questions --
answers that will lead to further clues to a theoretical understanding of
acoustic turbulence. We hope that the present study will stimulate research in
this direction.

>>>>

The shallow water (SW) equations  have been widely used to study basic
mechanisms occurring in geophysical flows \cite[see for
example][]{VallisLIVRE2006}.
%
The equations are based on the hydrostatic approximation which is
extremely well satisfied for a very wide range of scales in the oceans
and in the atmosphere.  They also rely on a stronger hypothesis
regarding the density stratification.  The fluid is assumed to be
structured in a limited number of thin homogeneous layers, which leads
to equations involving only two-dimensional operators. The two-layer
SW equations capture the baroclinic instability which is of
primary importance for the dynamics of the oceans and of the
atmosphere \cite[]{VallisLIVRE2006, Wirth2013}.
%
The single layer SW equations are very similar to
the two-dimensional compressible Navier-Stokes equations.  The
equations do not capture baroclinic instability but they constitute
one of the simplest hydrodynamic models with coexisting eigenmodes of
the linearized operator with zero linear frequency and with finite
non-zero linear frequency, $\omega = \pm\sqrt{f^2 + c^2
k^2}$, where $f$ is the Coriolis parameter, $c$ the gravity wave speed and $k
= |\kk|$ the wave number.
%

@@

Some predictions are based on the weak wave turbulence formalism
\cite[]{ZakharovLvovFalkovich1992, Nazarenko2011}. In the case of
inertia-gravity waves, \cite{FalkovichMedvedev1992} showed that the exact
solutions of the kinetic equation corresponding to a constant downscale energy
flux is associated with a spectrum scaling as $E(k) \sim k^{-8/3}$, while
\cite{ZakharovSagdeev1970} used weak turbulence formalism to derive a spectrum
of the form $ E(k) \sim k^{-3/2} $ for acoustic turbulence. This prediction is
of particular interest, since the acoustic equations and the SW equations are
identical when a first order expansion is made in density or displacement
perturbations. It may be questioned, however, that weak turbulence formalism is
applicable to acoustic and SW wave turbulence, no matter how weak the
nonlinearities are supposed to be. As pointed out by \cite{KadomtsevPet1970}
and \cite{FalkovichMeyer1996}, when dispersion is small enough, waves moving in
the same direction have the same velocity and interact strongly, which leads to
the formation of shocks. In this case, the weak wave turbulence formalism is
unable to give valuable results. Such sharp and long structures have been
observed in many simulations \cite[]{FargeSadourny1989,
PolvaniMcWilliamsSpallFord1994, LahayeZeitlin2012} but their effects are not
well understood.
%
As shown by \cite{Burgers1948} the energy spectrum of a flow dominated by
shocks will scale as $ k^{-2} $, a prediction which has been confirmed by a
great number of simulations of Burgers equation \cite[for a review, see ]
[]{Frisch2001}. The shocks also lead to very strong intermittency, as
demonstrated by \cite{BouchaudMezardParisi1995} and
\cite{WeinanKhaninMazelSinai1997} for Burgers turbulence.
%
\cite{FalkovichMeyer1996} simulated acoustic turbulence dominated by shocks
and reported spectra scaling as $ k^{-2} $.
\cite{YuanHamilton1994} carried out
forced dissipative simulations of the SW equations showing similar spectra.
However, the resolution in both these studies was quite coarse, ($386^2$
and $101^2$ grid points, respectively) so that the scaling range was very
narrow.  Moreover, \cite{FalkovichMeyer1996} used a very particular
type of strongly anisotropic forcing with waves in only one
direction while \cite{YuanHamilton1994} forced in geostrophic modes
which severely complicates the interpretation.

@@

We have carried out a theoretical and numerical investigation of SW wave
turbulence. First, we derived the SW analogue (\ref{eq_Kolmo}) of the
`four-fifths' law of Kolmogorov turbulence. Using this relation and
straightforward statistical and geometrical arguments we developed a simple
shock model predicting that the shock amplitude scales as $ (\epsilon d)^{1/3}
$, where $ d $ is the mean distance between the shocks, and that the $ p $:th
order structure function above a certain minimum will scale as $ (\epsilon
d)^{p/3} r/d $. Then, we carried out a series of twenty forced dissipative
simulations, varying the Froude number and the resolution. In all simulations,
a statistically stationary state were reached and in all simulations we
observed shocks. The flow variables in each Fourier mode were found to evolve
in accordance with linear wave dynamics, with equipartition between APE and KE
over a period. The third order structure function relation was fulfilled with a
high degree of accuracy. From the simulations we made two interesting
observations that fall outside the predictive range of the model. The first
observation was that mean energy in the stationary state approximately scales
as (\ref{MeanEnergy}), suggesting that the normalized dissipation
(\ref{Dissipation}) will go to zero both in the limit of small viscosity and
large wave speed. This is different from three dimensional Kolmogorov
turbulence as well as strongly stratified turbulence, where, in both cases,
dissipation is finite in the limit of small viscosity, and in the latter case
also is independent of the degree of stratification. This observation suggests
that SW wave turbulence does not fit into the paradigm of a local
Richardson-Kolmogorov cascade. The second observation we made was that the mean
distance between the shocks scales as $ c^{-1/2} $, if the other parameters are
held constant. As we increased $ c $, the shocks were thus becoming denser.
Using this observation we tested the shock model by plotting the normalized and
compensated structure functions of different orders. Generally we found that
there was a quite good agreement between the simulation results and the model
predictions, becoming better with decreasing wave speed and increasing
resolution.

@@

The question that originally motivated this study was if SW wave turbulence can
be used as a model for energy dissipation in the atmosphere and the oceans.
Undoubtedly, the answer to this question is negative and the reason for this is
not primarily the appearance of shocks and the associated $ k^{-2} $-spectrum
which is not consistent with the observed $ k^{-5/3} $-spectrum. The main
reason is that SW wave turbulence is a far too inefficient agent of
dissipation. Since the Reynolds number of geophysical flows is extremely large
and the stratification is strong, the relation (\ref{Dissipation}) implies that
dissipation would be absent in the interior of the atmosphere and the oceans
with SW turbulence as the responsible agent. This not what we observe.

Although the answer to the question that originally motivated this study is
negative, it may lead us or some other investigators to pursue another
interesting research direction. As pointed out in the introduction, the
acoustic equations are to the lowest order expansion in density perturbations
identical to the SW equations. This study may therefore give important clues to
the long standing problem of acoustic turbulence, in two and three dimensions.
A similar shock model as we developed in two dimensions may easily be
formulated in three dimensions, where the third order structure function law
will be similar to (\ref{eq_Kolmo}), with the only difference that the constant
$ 4 $ on the right hand side should be replaced by $ 8/3 $. In three dimensions
we find
\begin{equation}
\meane{ |\delta \uu|^2 \delta J_L }
+ c^2\meane{ (\delta h)^2 \delta u_L } = - \frac{8}{3} \varepsilon r. \label{eq_Kolmo3}
\end{equation}
In the case of acoustic turbulence $ \delta h $ should be interpreted as a
normalized density increment rather than a displacement increment. If shocks in
three dimensions are assumed to form as smooth surfaces rather than smooth
lines, then the mean distance, $ d $, between the shocks will appear in the
model as $ d \sim {\cal{V}}/A_s $, where $ A_{s} $ is the total shock area and
$ \cal{V} $ is the volume of the domain. The shock amplitude will thus scale as
$ (\epsilon d)^{1/3} $ and the structure functions will scale as $ (\epsilon
d)^{p/3} r/d $ also in three dimensions, provided, of course, that shocks will
form in a similar way as in two dimensions. If they do, the most interesting
questions are if the mean energy and the mean distance between the shocks scale
in a similar way in three dimensions as in two dimensions. Simulations or
experiments of acoustic turbulence may provide answers to these questions --
answers that will lead to further clues to a theoretical understanding of
acoustic turbulence. We hope that the present study will stimulate research in
this direction.

### 2018-10-23 Old_Latex/appendix_dissip_forcing.tex
Update Erik's files

>>>>

Since only the ageostrophic variable is forced ($\hat f_d = 0$),%
(i) only the thickness fluctuation $\eta$ is forced in the
non-rotating case and %
(ii) the force terms in (\ref{eqapmnum}) are simply equal to $\hat
f_\pm = \hat f_a/2$.
%
In order to compute the force $\hat f_a$, we start from a
pre-normalized force $\hat f_{0}$ obtained from a normal random
process decorrelated in time.
%
The force is then normalized such that the quadratic part of the total
energy $\langle|\uu|^2 + c^2 \eta^2\rangle/2$ is injected at a
constant rate.
%
The spectral injection rate of the quadratic energy averaged over one
time step is (see appendix~\ref{app_comp})
\begin{equation}
P_q(\kk, t) 
= 
\Re\{ \hat \uu(\kk)^* \cdot \hat \ff(\kk) 
+
c^2 \hat \eta(\kk)^* \hat f_\eta(\kk) \}
+ 
(|\hat\ff|^2 + c^2 |\hat f_\eta|^2) \delta t /2,
\end{equation}
where $\Re$ denotes the real part.
%
Writing $\hat f_a = \alpha \hat f_{0}$, it is straightforward to solve
a second-order equation for the coefficient $\alpha$ in order to fix
the injection rate $\Add{P_0 \equiv} \sum_\kk P_q(\kk, t)$ to unity.

### 2018-10-23 Old_Latex/section_advanced_theory.tex
Update Erik's files

We will now derive an analogue of the so called `four-fifths law'
\cite[]{Kolmogorov1941} for the the third order velocity structure function of
incompressible isotropic turbulence. In the case of irrotational shallow water
wave turbulence the analogous law contains a third order structure function
involving both velocity and displacement increments. In order for such a law to
exist it is necessary that the velocity field is either non-divergent
(incompressible) or irrotational. To derive the law it is convenient to start
from the following equations
\begin{eqnarray} \label{IRR}
\p_t \uu &=& -\bnabla \cdot (\uu \cdot \uu /2) - c^2 \bnabla h  \\
\p_t \JJ &=& -\p_j (u_j \JJ) - \bnabla E_p,\\
\p_t h   &=& -\bnabla \cdot \JJ \, ,
\end{eqnarray}
where we have used the assumption that the velocity field is irrotational in
(\ref{IRR}). We consider two points, positioned at $ \bf x $ and $ {\bf
x}^\prime $, separated by the vector $ {\bf r} = {\bf x}^\prime - {\bf x} $.
Using Cartesian tensor notation we denote derivates with respect to $ {\bf x} $
as $ \partial_i $ and derivatives with respect to $ {\bf x}^\prime $ as $
\partial^{\prime}_i $. Treating $ \bf x $ and $ {\bf x}^\prime $ as independent
variables we find

>>>>

We will now derive an analogue of the so called `four-fifths law'
\cite[]{Kolmogorov1941} for the the third order velocity structure function of
incompressible isotropic turbulence. In the case of irrotational shallow water
wave turbulence the analogous law contains a third order structure function
involving both velocity and displacement increments. In order for such a law to
exist it is necessary that the velocity field is either non-divergent
(incompressible) or irrotational. To derive the law it is convenient to start
from the following equations
\begin{eqnarray} \label{IRR}
\p_t \uu &=& -\bnabla \cdot (\uu \cdot \uu /2) - c^2 \bnabla h  \\
\p_t \JJ &=& -\p_j (u_j \JJ) - \bnabla E_p,\\
\p_t h   &=& -\bnabla \cdot \JJ \, ,
\end{eqnarray}
where we have used the assumption that the velocity field is irrotational in
(\ref{IRR}). We consider two points, positioned at $ \bf x $ and $ {\bf
x}^\prime $, separated by the vector $ {\bf r} = {\bf x}^\prime - {\bf x} $.
Using Cartesian tensor notation we denote derivatives with respect to $ {\bf x} $
as $ \partial_i $ and derivatives with respect to $ {\bf x}^\prime $ as $
\partial^{\prime}_i $. Treating $ \bf x $ and $ {\bf x}^\prime $ as independent
variables we find

### 2018-10-23 Old_Latex/section_basic_theory.tex
Update Erik's files

In a non-rotating system of reference the SW equations for a thin layer of fluid over a flat bottom and with a free
surface can be written as  \cite[see for example][]{VallisLIVRE2006}
\begin{eqnarray} \label{UEq}
\p_t \uu + \uu\cdot \bnabla  \uu   
&=& - c^2 \bnabla h + \frac{\nu}{h}  \bnabla^2 \uu,   \label{eq_uu}\\ \label{HEq}
\p_t   h    &=& - \bnabla \cdot (h \uu).  \label{eq_h}
\end{eqnarray}
where $\uu$ is the horizontal velocity, %
$h = 1 + \eta $ the non-dimensional thickness of the fluid layer,  $ \eta $ being the surface displacement, 
$\nu$ the kinematic viscosity and $ c $ is the gravity wave speed. The SW equations conserve mass, $ h $, and momentum $ {\bf J} = h{\bf u} $. As a matter of fact, we have constructed the viscous term in (\ref{UEq}) in such a way that momentum is conserved and energy dissipation is positive definite. This can only be accomplished by permitting the term to be nonlinear in the flow variables. There are different forms of nonlinear terms that fulfill both conditions and it may be disputed which is the best one. However, in the simulations we will use diffusion terms in both (\ref{UEq}) and (\ref{HEq}) that will not fulfill any of these two conditions in a strict sense. Therefore, we will not discuss this matter further. The inviscid SW equations conserve a local
quantity along trajectories of the fluid particles, the Ertel
potential vorticity $\ErtelPV = \zeta /h$, where $\zeta  $ is the vorticity, which in a rotating system should be interpreted as absolute vorticity. In this paper this conservation law will be of no relevance since we only consider
irrotational flows for which the velocity can be written as $ \uu = \bnabla \phi $ , where $ \phi $ is the velocity potential. In a domain with no net fluxes through the boundaries the inviscid equations conserve total energy $ E_K + E_P $, where $ E_K =   {\bf J}  \cdot {\uu} /2 $ is kinetic energy and $ E_P = c^{2} h^2/2 $ is potential energy. The latter can be split into three terms as \begin{equation}
E_P = c^2/2 + c^2\eta+ c^2 \eta^2/2, 
\end{equation}
where the first term corresponds the potential energy of the state with no
surface displacement.  The third term, which is quadratic in the surface displacement, may be named available potential energy (APE),
$E_A = c^2\eta^2/2$, a concept introduced by  \cite{Lorenz1955}. As a consequence of mass and energy conservation the SW equations also conserve the sum of kinetic and available potential energy, $ E_K + E_A $.
 The velocity potential and the displacement of the linearized inviscid SW equations both satisfy the wave equation,
\begin{equation}
\frac{\partial ^2 \eta}{\partial t^2} = c^2 \nabla^2 \eta \, ,
\end{equation}
with equipartition between KE and APE over a wave period in each Fourier mode.

>>>>

In a non-rotating system of reference the SW equations for a thin layer of fluid over a flat bottom and with a free
surface can be written as  \cite[see for example][]{VallisLIVRE2006}
\begin{eqnarray} \label{UEq}
\p_t \uu + \uu\cdot \bnabla  \uu
&=& - c^2 \bnabla h + \frac{\nu}{h}  \bnabla^2 \uu,   \label{eq_uu}\\ \label{HEq}
\p_t   h    &=& - \bnabla \cdot (h \uu).  \label{eq_h}
\end{eqnarray}
where $\uu$ is the horizontal velocity, $h = 1 + \eta $ the non-dimensional
thickness of the fluid layer, $ \eta $ being the surface displacement, $\nu$
the kinematic viscosity and $ c $ is the gravity wave speed. The SW equations
conserve mass, $ h $, and momentum $ {\bf J} = h{\bf u} $. As a matter of fact,
we have constructed the viscous term in (\ref{UEq}) in such a way that momentum
is conserved and energy dissipation is positive definite. This can only be
accomplished by permitting the term to be nonlinear in the flow variables.
There are different forms of nonlinear terms that fulfill both conditions and
it may be disputed which is the best one. However, in the simulations we will
use diffusion terms in both (\ref{UEq}) and (\ref{HEq}) that will not fulfill
any of these two conditions in a strict sense. Therefore, we will not discuss
this matter further. The inviscid SW equations conserve a local quantity along
trajectories of the fluid particles, the Ertel potential vorticity $\ErtelPV =
\zeta /h$, where $\zeta $ is the vorticity, which in a rotating system should
be interpreted as absolute vorticity. In this paper this conservation law will
be of no relevance since we only consider irrotational flows for which the
velocity can be written as $ \uu = \bnabla \phi $ , where $ \phi $ is the
velocity potential. In a domain with no net fluxes through the boundaries the
inviscid equations conserve total energy $ E_K + E_P $, where $ E_K = {\bf J}
\cdot {\uu} /2 $ is kinetic energy and $ E_P = c^{2} h^2/2 $ is potential
energy. The latter can be split into three terms as
\begin{equation}
E_P = c^2/2 + c^2\eta+ c^2 \eta^2/2,
\end{equation}
where the first term corresponds the potential energy of the state with no
surface displacement. The third term, which is quadratic in the surface
displacement, may be named available potential energy (APE), $E_A =
c^2\eta^2/2$, a concept introduced by \cite{Lorenz1955}. As a consequence of
mass and energy conservation the SW equations also conserve the sum of kinetic
and available potential energy, $ E_K + E_A $. The velocity potential and the
displacement of the linearized inviscid SW equations both satisfy the wave
equation,
\begin{equation}
\frac{\partial ^2 \eta}{\partial t^2} = c^2 \nabla^2 \eta \, ,
\end{equation}
with equipartition between KE and APE over a wave period in each Fourier mode.
